
\chapter{ESPACENET}
\label{chap:espacenet}

\section{IPC A01D 46/00}
\label{sec:ipc-a01d-4600}

\subsection{Harvesting AND Selective}
\label{sec:harvesting-selective}


\PatenteESPACENET{Automated selective harvesting of crops with continuous
  offload}% Titulo da Patente
{US2016157431 (A1)}% Numero da Patente
{2016-06-09}% Data da Patente
{A system including a picking apparatus including a plurality of grippers each
  spaced apart and extending radially from a central axis of the picking
  apparatus, and each configured to pick a different individual crop of crops of
  plants. The picking apparatus can be configured to use a first one of the
  plurality of grippers to pick a first individual crop of the crops at a first
  time. During a second time period that starts with a second one of the
  plurality of grippers picking a second individual crop of the crops and ends
  with a third one of the plurality of grippers picking a third individual crop
  of the crops, the picking apparatus can be configured to offload the first
  individual crop from the first one of the plurality of grippers. The second
  time period can start after the first time. The second and third ones of the
  plurality of grippers can be configured to hold the second and third
  individual crops, respectively, at the end of the second time period. Other
  embodiments are provided.}% Abstract
{patente-espacenet-01}% Figura

\PatenteESPACENET{Improvements to selective tea plucking}% Titulo da Patente
{IN9264DEN2014 (A)}% Numero da Patente
{2015-07-10}% Data da Patente
{Apparatus for selectively harvesting plant material particularly the leaves and
  bud of a plant having a stem such as a tea plant is provided.  The apparatus
  includes a conveyor belt (5) plant engaging members (20) movable relative to
  the conveyor belt (5) to trap the plant matter between the conveyor belt (5)
  and the plant engaging members (20) at a first level and a stem engaging
  member (11) arranged to contact a stem of the plant at a predetermined second
  level lower than the first wherein when the stem of trapped plant material
  extending above the predetermined second level is broken by the stem engaging
  member (11) to harvest the trapped plant material. In one embodiment the stem
  engaging member is a breaker bar (11). In an alternative embodiment the stem
  engaging member is a cable wire or cord maintained in tension at the
  predetermined second level.}% Abstract
{patente-espacenet-02}% Figura

\PatenteESPACENET{Automated selective harvesting of crops}% Titulo da Patente
{EP3082397 (A1)}% Numero da Patente
{2016-10-26}% Data da Patente
{Various embodiments include a device for selectively harvesting crops on a
  plant. The device can include a picking apparatus.  The picking apparatus can
  be rotatable around a central axis. The picking apparatus can include a
  plurality of grippers each spaced apart and extending radially from the
  central axis, and each configured to pick a different individual one of the
  crops. Each of the plurality of grippers can be adjustable between an open
  position and a closed position. Each of the plurality of grippers can be
  configured in the open position to open around the individual crop. Each of
  the plurality of grippers can be configured in the closed position to securely
  hold the individual crop when the picking apparatus is rotated around the
  central axis. Other embodiments are provided.}% Abstract
{}% Figura (Pode ficar vazio)


\subsection{Harvesting AND Coffee}
\label{sec:harvesting-coffee}

\PatenteESPACENET{Mobile harvester}% Titulo da Patente
{WO2008156703 (A1)}% Numero da Patente
{2008-12-24}% Data da Patente
{Systems, including apparatus and methods, for harvesting a
product with a mobile harvester so as to minimize the amount of product
lost during harvesting. The disclosed systems include an array of catcher
plates designed to surround a plant to be harvested, in a manner that
minimizes the possibility of harvested product dropping through the plates
to the ground and thus being lost. These systems may be useful for
harvesting a wide variety of products that grow on plants such as trees or
bushes, including without limitation berries, fruit, and coffee beans.}% Abstract
{patente-espacenet-03}% Figura


\section{IPC A01D 46/06}
\label{sec:ipc-a01d-4606-1}


\subsection{Harvesting AND Selective}
\label{sec:harvesting-selective-1}


\PatenteESPACENET{Portable device for selective harvest with identification of
  the fruit by colour}% Titulo da Patente
{WO2015121809 (A1)}% Numero da Patente
{2015-08-20}% Data da Patente
{The invention relates to a portable device for selective harvest and to a
  method for identifying fruit and selectively harvesting coffee fruit or other
  fruit. The portable device for selectively harvesting fruit on a branch
  comprises: an image acquisition system (1), an image processing system, a
  picking mechanism (2), a control system, a receiving mechanism, and a system
  for powering the device, the device also comprising a servo-vision system. The
  method for identifying fruit by colour and selective harvest comprises the
  steps of: (a) acquiring images of the fruit on the branch; (b) storing the
  images in a memory; (c) preprocessing the images with a filtering operation in
  order to reduce noise and improve the images; (d) converting, in the images,
  the RGB colour to a LUX mod colour space; (e) thresholding the variables U and
  modifiedVLUX of the LUX mod colour space, obtaining a binary image, and
  detecting the pixels of ripe and unripe fruit; (f) counting the pixels of ripe
  and unripe fruit; (g) detecting the areas of interest, according to the
  position on the branch comprising the fruit, which is indicated by the image;
  (h) determining a threshold value relating to the risk of picking unripe fruit
  "N" as a percentage of the totality of the section of the area of interest;
  (i) determining the risk of picking unripe fruit by comparing the percentage
  of pixels of unripe fruit in the section of the area of interest with the
  threshold value relating to the risk of picking unripe fruit "N"; and (j)
  generating a command for activation and picking of the fruit according to the
  rules for the activation for picking fruit.}% Abstract
{patente-espacenet-04}% Figura

\subsection{Harvesting AND Coffee}
\label{sec:harvesting-coffee-1}

\PatenteESPACENET{Raspberry, coffee picking machine}% Titulo da Patente
{CN205105662 (U)}% Numero da Patente
{2016-03-30}% Data da Patente
{The utility model relates to an agricultural machine field is specifically said
  to relate to a raspberry, coffee picking machine. The utility model provides a
  raspberry, coffee picking machine, organize (1), storage battery knapsack (2),
  electric wire (3), speed governing switch (4), handle (5), hangers (6), magnet
  (7), baffle (8), roller shaft (9), silica gel running roller (10), silica gel
  blade (11), gear box (12), buncher (13) including the lithium cell storage
  battery. The utility model provides a raspberry, coffee picking machine uses
  charge battery's form, makes the complete machine lightly can take, be
  provided with buncher and speed governing switch, make and freely to adjust
  the rotational speed of gyro wheel, improved the fruit and received clean
  rate, reduced the fruit and hindered the fruit rate, the hardness of using the
  silica gel blade can not change along with the change of temperature, makes
  complete machine harvesting performance more stable.}% Abstract
{patente-espacenet-05}% Figura

% \PatenteESPACENET{Titulo}% Titulo da Patente
% {Numero Patente}% Numero da Patente
% {Data Patente}% Data da Patente
% {\textit{Abstract} da patente ...}% Abstract
% {}% Figura


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../template-01"
%%% End:
